### 2010-03-31 papers/icfp-2010-desc/paper_idesc.tex
Desc@ICFP: explain where \overbar comes from
Desc@ICFP: demote \subsubsection{Indexed Tagged Description}
Desc@ICFP: introduce inductionI and AllI for indexed descriptions
Desc@ICFP: clean-up \note{}s

\[\stkl{
\Rule{\Gamma \vdash \Bhab{\V{I}}{\Set} \qquad
      \Gamma \vdash \Bhab{\V{R}}{\V{I} \To \IDesc{\V{I}}}}
     {\Gamma \vdash \Bhab{\IMu{\V{I}}{\V{R}}{\!}}{\V{I}\To\Set}} \qquad
\\:\
\Rule{\begin{array}{l@{\qquad}l}
          \Gamma \vdash \Bhab{\V{I}}{\Set} &
          \Gamma \vdash \Bhab{\V{R}}{\V{I} \To \IDesc{\V{I}}} \\
          \Gamma \vdash \Bhab{\V{i}}{\V{I}} &
          \Gamma \vdash \Bhab{\V{x}}{\idescop{\V{R}\:\V{i}}{\V{I}}{(\IMu{\V{I}}{\V{R}}{\!})}}
      \end{array}}
     {\Gamma \vdash \Bhab{\Con{\V{x}}}{\IMu{\V{I}}{\V{R}}{\V{i}}}}
}\]

@@

@@

\note{Should we say something about IMu, fixed-points, and their
  elimination before moving on? If so, where should we put it?}

@@

\subsubsection{Tagged Indexed Descriptions}

@@

The type of $\F{eval}$ is strikingly similar to a
catamorphism. Indeed, implementing a single step of evaluation -- the
algebra -- is sufficient, as $\F{cataI}$ \note{We have not defined
  \F{cataI}!} gives, for free, the full evaluator. The implementation
is as follows:

>>>>

\[\stkl{
\Rule{\Gamma \vdash \Bhab{\V{I}}{\Set} \qquad
      \Gamma \vdash \Bhab{\V{R}}{\V{I} \To \IDesc{\V{I}}}}
     {\Gamma \vdash \Bhab{\IMu{\V{I}}{\V{R}}{\!}}{\V{I}\To\Set}} \qquad
\\
\Rule{\begin{array}{l@{\qquad}l}
          \Gamma \vdash \Bhab{\V{I}}{\Set} &
          \Gamma \vdash \Bhab{\V{R}}{\V{I} \To \IDesc{\V{I}}} \\
          \Gamma \vdash \Bhab{\V{i}}{\V{I}} &
          \Gamma \vdash \Bhab{\V{x}}{\idescop{\V{R}\:\V{i}}{\V{I}}{(\IMu{\V{I}}{\V{R}}{\!})}}
      \end{array}}
     {\Gamma \vdash \Bhab{\Con{\V{x}}}{\IMu{\V{I}}{\V{R}}{\V{i}}}}
}\]

@@

The induction scheme on $\IDesc{\!}$ has the following type:

\[
\begin{array}{@{}ll}
\F{inductionI} : & _{\Bhab{\V{I}}{\Set}}
                   \PITEL{\V{R}}{\V{I} \To \IDesc{\V{I}}}
                   \PI{\V{P}}{\SIGMA{\V{i}}{\V{I}} \IMu{\V{I}}{\V{R}}{\!} \To \Set} \\
                 & (      \PITEL{\V{i}}{\V{I}} 
                          \PI{\V{xs}}{\idescop{\V{R}\: \V{i}}{\V{I}}{\IMu{\V{I}}{\V{R}}{\!}}} \\
                 & \   \idescop{\AllI{\V{I}}
                                     {(\V{R}\: \V{i})}
                                     {(\IMu{\V{I}}{\V{R}}{\!})}
                                     {\V{xs}}}
                               {}
                               {\V{P}} \To
                       \V{P}\: \pair{\V{i}}{\Con{\V{xs}}}{}) \\
                 & \PITEL{\V{i}}{\V{I}}
                   \PI{\V{x}}{\IMu{\V{I}}{\V{R}}{\V{i}}}
                   \V{P}\: \pair{\V{i}}{\V{x}}{}
\end{array}
\]

Where the operator $\AllI{\!}{\!}{\!}{\!}$ is of type:

\[
\AllI{\!}{\!}{\!}{\!} : _{\Bhab{\V{I}}{\Set}}
                        \PITEL{\V{D}}{\IDesc{\V{I}}}
                        \PI{\V{P}}{\V{I} \To \Set}
                        \idescop{\V{D}}{\V{I}}{\V{P}} \To
                        \IDesc{(\SIGMA{\V{i}}{\V{I}} \V{P})} 
\]

The implementation of these operators can be found in the companion
technical report. As for descriptions, we can compute a generic
catamorphism, $\F{cataI}$, from $\F{inductionI}$.

@@

@@

\paragraph{Tagged Indexed Descriptions:}

@@

The type of $\F{eval}$ is strikingly similar to a
catamorphism. Indeed, implementing a single step of evaluation -- the
algebra -- is sufficient, as $\F{cataI}$ gives, for free, the full
evaluator. The implementation is as follows:
